### 2022-09-27 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@16217d2fa569fdf41fb11fee129c94289230ab70 🚀

It is important to recall that a metaweb is intended as a catalogue of
all potential interactions, which is then filtered for a given
application (Morales-Castilla et al., 2015). In a sense, that most
ecological interactions are elusive can call for a slightly different
approach to sampling: once the common interactions are documented, the
effort required in documenting each rare interaction will increase
exponentially. Recent proposals suggest that machine learning
algorithms, in these situations, can act as data generators (Hoffmann et
al., 2019): high quality observational data can generate the core rules
underpinning the network structure, and be supplemented with synthetic
data coming from predictive models, increasing the volume of information
available for inference. Indeed, Strydom, Catchen, et al. (2021)
suggested that knowing the metaweb may render the prediction of local
networks easier, because it fixes an ``upper bound'' on which
interactions can exist. In this context, a probabilistic metaweb
represents an aggregation of informative priors on the interactions,
elusive information with the potential to boost our predictive ability
(Bartomeus et al., 2016).

>>>>

It is important to recall that a metaweb is intended as a catalogue of
all potential interactions, which is then filtered for a given
application (Morales-Castilla et al., 2015). In a sense, that most
ecological interactions are elusive can call for a slightly different
approach to sampling: once the common interactions are documented, the
effort required in documenting each rare interaction will increase
exponentially. Recent proposals suggest that machine learning algorithms
can also act as data generators (Hoffmann et al., 2019): high quality
observational data can be used to infer core rules underpinning network
structure, and be supplemented with synthetic data coming from
predictive models trained on them, thereby increasing the volume of
information available for analysis. Indeed, Strydom, Catchen, et al.
(2021) suggested that knowing the metaweb may render the prediction of
local networks easier, because it fixes an ``upper bound'' on which
interactions can exist. In this context, a probabilistic metaweb
represents an aggregation of informative priors on the interactions,
elusive information with the potential to boost our predictive ability
(Bartomeus et al., 2016).
